---
title: "Forecasting modeling in R"
author: "Olga Berezovsky"
date: "10/24/2016"
output: html_document
params:
  minimum: 
    label: "Minimum:"
    value: 100
    input: slider
    min: 0
    max: 1000
  region:
    label: "Region:"
    value: east
    input: select
    choices: [east, west, north, south]
  data: 
    label: "Input dataset:"
    value: results.csv
    input: file
---

# Forecasting modeling in R

Building predictions is one of the most common tasks in data analytics. Below I am going to describe time series analysis and projection based on the chronological raw data. 

**Dataset**: I’m going to use Google BigQuery public data — github_nested table 
**The task**: project the amount of daily repositories in 2013 based on the 2010–2012 available data.

-----------------------------------------

## The process
- Acquire data from Google BigQuery
- Clean/transform data into numerical and date properties
- Run *forecast*
- Plot forecast results

### Acquiring data set
In order to connect to the Google BigQuery I am using  [bigQueryR](https://cran.r-project.org/web/packages/bigQueryR/vignettes/bigQueryR.html) package.

```{r Acquiring dataset, echo=FALSE}

library(bigQueryR)

#Authenticate to Google BigQuery
bqr_auth()

dataset <- bqr_query("driven-strength-147321",
                     "samples",
                     "SELECT DATE(repository_created_at) as day,
                      count(distinct(repository_url)) as cnt
                      FROM [bigquery-public-data:samples.github_timeline]
                      WHERE repository_created_at IS NOT NULL
                      GROUP BY 1
                      ORDER BY 1 asc")


```
### Cleaning/transforming data
```{r Cleaning}
head(dataset, 10)
#In order to run a forecast we need to have 2 columns with date and intereger data types. Lets check what datatypes we have:
class(dataset$day)
dataset$day <- as.Date(dataset$day)
class(dataset$day)
class(dataset$cnt)
#lets substract a dataframe for buiding a forecast
head(dataset, 1440) -> dataset1
tail(dataset1, 5)
```

```{r Forecasting}
#I'm going to use exponential smoothing methods for a short-term forecasts 
library(forecast)

#fit_arima <- auto.arima(dataset$rolling_count)
#f_arima <- forecast(fit_arima,h=24*14,level=80)

```
-----------------------

### Prediction

